\textsf{Are large language models superhuman chemists?}

### 2024-03-26 src/tex/appendix.tex
nice mae vs. number atoms for NMR

>>>>

\subsection{Performance as a function of molecular features}

\begin{figure}
    \centering
    \includegraphics{figures/correlation_plot_is_number_nmr_peaks_num_atoms.pdf}
    \caption{\textbf{Impact of the mean absolute error in the prediction of number of NMR peaks on the number of atoms.}}
    \script{correlate_with_molecule_features.py}
    \label{fig:correlation_plot_is_number_nmr_peaks_num_atoms}
\end{figure}

### 2024-03-26 src/tex/showyourwork-metadata.tex
nice mae vs. number atoms for NMR

        \OnGithubActionsfalse
        \def\syw@url{https://github.com/lamalab-org/chembench-paper}
    \def\syw@slug{lamalab-org/chembench-paper}
    \def\syw@sha{9e3e1d5a5f3dc81ac1ab792b79e58cce26f6bbda}
    \def\syw@runid{}

@@

        \addvalue{fig:topic_barplot_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:wordcloud_script}{src/scripts/wordcloud.py}
        \addvalue{fig:human_timing_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:experience_vs_correctness_script}{src/scripts/analyze_human_data.py}

        \addvalue{output/total_number_of_questions.txt_rule}{Snakefile\#L1}
        \addvalue{output/manually_generated.txt_rule}{Snakefile\#L1}
        \addvalue{output/automatically_generated.txt_rule}{Snakefile\#L1}
        \addvalue{output/number_experts.txt_rule}{Snakefile\#L20}
        \addvalue{output/total_hours.txt_rule}{Snakefile\#L20}
        \addvalue{output/flesch_kincaid_reading_ease.txt_rule}{Snakefile\#L30}
        \addvalue{output/num_h_statements.txt_rule}{Snakefile\#L1}
        \addvalue{output/num_pictograms.txt_rule}{Snakefile\#L1}
        \addvalue{output/num_dai.txt_rule}{Snakefile\#L1}
        \addvalue{output/spearman_experience_score.txt_rule}{Snakefile\#L20}
        \addvalue{output/spearman_experience_score_p.txt_rule}{Snakefile\#L20}

>>>>

        \OnGithubActionsfalse
        \def\syw@url{https://github.com/lamalab-org/chembench-paper}
    \def\syw@slug{lamalab-org/chembench-paper}
    \def\syw@sha{e9da465b586df3b66d049cbdbf915503a23b2cb2}
    \def\syw@runid{}

@@

        \addvalue{fig:topic_barplot_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:question_diversity_script}{src/scripts/plot_question_diversity.py}
        \addvalue{fig:human_vs_models_bar_script}{src/scripts/plot_overview_performance_plot.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_human_script}{src/scripts/analyze_model_reports.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_human_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:confidence_vs_performance_script}{src/scripts/joint_analysis_confidence_performance.py}
        \addvalue{fig:flesch_kincaid_reading_ease_script}{src/scripts/wordcloud.py}
        \addvalue{fig:question_count_barplot_mcq_vs_general_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:barplot_all_correct_all_questions_script}{src/scripts/plot_overview_performance_plot.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_overall_script}{src/scripts/analyze_model_reports.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_overall_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:parallel_coordinates_overall_script}{src/scripts/make_parallel_coordinates_plot.py}
        \addvalue{fig:parallel_coordinates_tiny_script}{src/scripts/make_parallel_coordinates_plot.py}
        \addvalue{fig:performance_per_topic_script}{src/scripts/analyze_performance_per_source.py}
        \addvalue{fig:performance_per_topic_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:performance_per_topic_tiny_script}{src/scripts/analyze_performance_per_source.py}
        \addvalue{fig:performance_per_topic_tiny_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:reading_ease_vs_model_performance_script}{src/scripts/reading_ease_vs_model_performance.py}
        \addvalue{fig:reading_ease_vs_model_performance_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:correlation_plot_is_number_nmr_peaks_num_atoms_script}{src/scripts/correlate_with_molecule_features.py}
        \addvalue{fig:human_score_distribution_script}{src/scripts/plot_human_score_distribution.py}
        \addvalue{fig:human_timing_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:experience_vs_correctness_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:confidence_score_distributions_script}{src/scripts/plot_confidence_score_distributions.py}

        \addvalue{output/total_number_of_questions.txt_rule}{Snakefile\#L20}
        \addvalue{output/manually_generated.txt_rule}{Snakefile\#L20}
        \addvalue{output/automatically_generated.txt_rule}{Snakefile\#L20}
        \addvalue{output/number_experts.txt_rule}{Snakefile\#L89}
        \addvalue{output/num_topics.txt_rule}{Snakefile\#L75}
        \addvalue{output/mcq_questions.txt_rule}{Snakefile\#L20}
        \addvalue{output/non_mcq_questions.txt_rule}{Snakefile\#L20}
        \addvalue{output/num_tiny_questions.txt_rule}{Snakefile\#L20}
        \addvalue{output/subset_scores/is_number_nmr_peaks_gpt4.txt_rule}{Snakefile\#L184}
        \addvalue{output/human_subset_scores/is_number_nmr_peaks.txt_rule}{Snakefile\#L184}
        \addvalue{output/subset_scores/is_gfk_gpt4.txt_rule}{Snakefile\#L184}
        \addvalue{output/subset_scores/is_gfk_claude3.txt_rule}{Snakefile\#L184}
        \addvalue{output/human_subset_scores/is_gfk.txt_rule}{Snakefile\#L184}
        \addvalue{output/model_confidence_performance/gpt4_is_pictograms_average_confidence_correct_overall.txt_rule}{Snakefile\#L273}
        \addvalue{output/model_confidence_performance/gpt4_is_pictograms_num_correct_overall.txt_rule}{Snakefile\#L273}
        \addvalue{output/model_confidence_performance/gpt4_is_pictograms_average_confidence_incorrect_overall.txt_rule}{Snakefile\#L273}
        \addvalue{output/model_confidence_performance/gpt4_is_pictograms_num_incorrect_overall.txt_rule}{Snakefile\#L273}
        \addvalue{output/model_confidence_performance/claude3_is_pictograms_average_confidence_correct_overall.txt_rule}{Snakefile\#L273}
        \addvalue{output/model_confidence_performance/claude3_is_pictograms_average_confidence_incorrect_overall.txt_rule}{Snakefile\#L273}
        \addvalue{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_combustion_engineering.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_ac_faessler_tum.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_pum_tum.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_icho.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_materials_synthesis.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_organic_reactivity.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_oup.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_safety.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_materials_compatibility.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_blac_gfk.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_reactive_groups.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_oxidation_states.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_electron_counts.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_number_of_isomers.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_point_group.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_smiles_to_name.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_name_to_smiles.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_pictograms.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_h_statements.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_dai.txt_rule}{Snakefile\#L235}
        \addvalue{output/num_users_with_education_info.txt_rule}{Snakefile\#L89}
        \addvalue{output/num_human_phd.txt_rule}{Snakefile\#L89}
        \addvalue{output/num_human_postdoc.txt_rule}{Snakefile\#L89}
        \addvalue{output/num_human_master.txt_rule}{Snakefile\#L89}
        \addvalue{output/num_human_bachelor.txt_rule}{Snakefile\#L89}
        \addvalue{output/num_humans_with_more_than_100_scores.txt_rule}{Snakefile\#L39}
        \addvalue{output/num_humans_with_204_scores.txt_rule}{Snakefile\#L39}
        \addvalue{output/spearman_experience_score.txt_rule}{Snakefile\#L89}
        \addvalue{output/spearman_experience_score_p.txt_rule}{Snakefile\#L89}
